---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Carl Wilson"
date: "8/29/2019"
output: 
  html_document: 
    fig_height: 10
    fig_width: 10
    highlight: espresso
    theme: simplex
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

(1640 rows by 3 columns (1 for each variable))

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
The shape of the data is non-linear, and there is a weak and negative linear relationship between x and y.
r = -.0645
### Exercise 3

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
 
ggplot(data = star_data, mapping = aes(x = x, y = y)) + 
  geom_point()
```

r = -0.0630
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
### Exercise 4

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
 
ggplot(data = circle_data, mapping = aes(x = x, y = y)) + 
  geom_point()
```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
r = -0.06834336	
### Exercise 5

```{r plot-all}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
geom_point() +
facet_wrap(~ dataset, ncol = 3) +
theme(legend.position = "none")
```
```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset)%>%
  summarize(r = cor(x, y))
print(13)
```
(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)